\chapter*{Epilogue}
\phantomsection
\addcontentsline{toc}{chapter}{Epilogue. What Makes a Good Systematic Trader?}
\markboth{Epilogue}{Epilogue}
\bichaptertitle{尾声}

TO FINISH THE BOOK I'D LIKE TO SUMMARISE WHAT I THINK ARE the main qualities a good systematic trader or investor should have.

在本书结束之际，我想总结一下：在我看来，一个优秀的系统化交易者或投资者应当具备哪些主要品质。

A systematic trader should be humble, and underestimate their intelligence, skill and luck. Assume your trading will go badly, be prepared for that eventuality, and be pleasantly surprised if it doesn't. Don't try anything too clever; it is probably unnecessary and it's more likely to go wrong.

系统化交易者应该保持谦逊，低估自己的智力、技能和运气。要假设你的交易会进展不顺，并为这种结果做好准备；如果事情没有那么糟，那就把它当作额外惊喜。
不要尝试过于聪明复杂的东西；那多半并无必要，而且更容易出错。

Use simple trading rules that have not been over-fitted or even fitted at all; constant no-rule forecasts, or discretionary forecasts combined with a strict stop loss policy. The handcrafting method of portfolio optimisation is both simple and effective.

应当使用简单的交易规则，这些规则不要过拟合，甚至最好根本不去拟合；比如恒定的“无规则”预测，或者将主观预测与严格止损政策结合起来。
手工构造式的投资组合优化方法，既简单又有效。

You should be sceptical. Do not trust anybody. Don't trust the broker encouraging you to trade more, the trainer peddling you an expensive course, or the author\footnote{This includes me.\par 这也包括我。} with a trading system that apparently worked for them, but might not be right for you.

你应该保持怀疑。不要轻信任何人。不要相信那个鼓励你多交易的经纪商，不要相信兜售高价课程的培训师，也不要相信某位作者，
哪怕他的交易系统看起来确实对他有效，却未必适合你。

Be pessimistic. Do not trust back-tests, even if you haven't over-fitted them, and even if they've been done on a rolling out of sample basis. The future is unlikely to be quite as good as the past. In my opinion a highly diversified system of systematic trading rules is unlikely to beat a Sharpe ratio (SR) of 1.0. If you're a semi-automatic trader who can't back-test their system, or an asset allocating investor with a static portfolio, then you should be even more pessimistic and assume maximum Sharpes of 0.5 and 0.4 respectively. You may do better, but you shouldn't expect to.

你还应该悲观。不要迷信回测，即便你没有对它过拟合，即便它还是用滚动样本外的方式完成的。未来不太可能和过去一样好。
在我看来，一套高度分散化的系统化交易规则组合，其夏普比率（SR）不太可能超过 1.0。如果你是无法回测自己系统的半自动交易者，
或者是持有静态投资组合的资产配置型投资者，那么你就应该更加悲观，分别把最大夏普假定为 0.5 和 0.4。你也许会做得更好，但你不应该预期自己一定能做到。

If you're making, or expect to make, steady gains with very few losses then there is a good chance you have a negative skew trading style which hasn't yet blown up, but probably will eventually. Adjust your percentage volatility target accordingly.

如果你现在，或者预期自己将来，会以极少亏损换来平稳持续的收益，那么很有可能你采用的是一种负偏度交易风格。它现在也许还没爆掉，但最终大概率会。
因此，你应当据此调整自己的百分比波动率目标。

A good systematic investor will be thoughtful. You should know why you might be making money and why you might not. Understand your markets and your trading rules.

一个优秀的系统化投资者应当善于思考。你应该知道自己为什么可能赚钱，也应该知道自己为什么可能赚不到钱。你必须理解自己所处的市场，也必须理解自己的交易规则。

Thriftiness is another virtue. Know your trading costs. Stick to speed limits: I recommend you set your turnover so you never spend more than a third of the pessimistic expected Sharpe ratio for each trading subsystem on trading costs. Don't make your broker, or market makers, any wealthier.

节俭是另一项美德。你必须清楚自己的交易成本。要遵守“限速”：我建议你把换手率控制到这样一个水平，即对每一个交易子系统而言，
你花在交易成本上的代价，永远不要超过其悲观预期夏普比率的三分之一。不要让你的经纪商或做市商因为你而变得更富有。

You should be nervous. Only commit trading capital you can afford to lose. Use HalfKelly: your maximum percentage volatility target should be half what you pessimistically expect your Sharpe ratio to be. At some point some instruments or trading rules in your portfolio will go badly wrong. Limit your exposure to this by trading the most diversified set of instruments and rules that you can. Stay away from low volatility instruments -- they're expensive to trade and dangerous.

你还应该保持警惕。只投入那些你输得起的交易资本。使用 HalfKelly：你的最大百分比波动率目标，应当设为你悲观预期夏普比率的一半。
在某个时刻，你投资组合中的某些品种或某些交易规则一定会出大问题。要通过尽可能交易最分散的一组品种和规则来限制这种暴露。
远离低波动工具 --- 它们交易起来成本高，而且危险。

The best systematic traders will be diligent when creating their systems, but lazy when running them. Put the hard work into designing a safe system that you are comfortable with and then do not change it. Make a commitment: don't be tempted to meddle, improve or risk manage. These time-consuming activities usually destroy performance.

最优秀的系统化交易者，在创建系统时应当勤奋，而在运行系统时应当懒惰。把真正的辛苦用在设计一套安全、让你安心的系统上，然后就不要再改它。
做出承诺：不要被诱惑去干预、去“改进”、去额外做风险管理。这些耗时的活动通常都会破坏表现。

Finally to make money you need to be lucky. Even if you do everything right you could still be unprofitable if the chance turns against you. You can't entirely eliminate risk from investing but you should quantify it, and make sure you can cope with the likely downside. So it only remains for me to say: Good Luck!

最后，想赚钱，你还需要一点运气。即便你把所有事情都做对了，如果运气站在你的对立面，你仍然可能赚不到钱。你无法把投资中的风险彻底消除，
但你应该把它量化出来，并确保自己能够承受最可能发生的下行结果。所以，最后我只剩下一句话要说：祝你好运！
