\chapter*{Acknowledgements}
\phantomsection
\addcontentsline{toc}{chapter}{Acknowledgements}
\markboth{Acknowledgements}{Acknowledgements}

This book only exists because I spent seven years at AHL learning the craft of systematic trading, although there are no corporate secrets revealed here (as their lawyers will be pleased to know). I wouldn't have been able to write this without spending most of a decade immersed amongst a group of people who almost uniquely in the finance industry managed to be incredibly clever and successful, whilst still being fantastically nice and interesting people to work with.

There are many people I'd like to thank individually who worked, or still work, at AHL, their parent company the Man Group, and their research centre the Oxford Man Institute; but it would take another book to do it. You know who you are.

I'd like to thank my friend Pietro Parodi for his feedback on early drafts of the theoretical chapters where his outside expert viewpoint was invaluable. One former AHL colleague I will mention by name is Thomas Smith. Whilst launching his own hedge fund, Thomas still found the time to spend dozens of unpaid hours reviewing drafts of my work, and behaved exactly like he did when we worked together; he was never afraid of telling me when I had written something that was unintelligible, meaningless, pointless or wrong (and sometimes all of those at the same time).

I'm very thankful to Stephen Eckett at Harriman House for discerning the seed of an interesting idea in amongst the turgid ramblings of my original proposal. My editor Craig Pearce has managed the difficult job of reassuring me that I've written a good book, whilst also politely suggesting how it could be improved.

Last, but certainly not least, I'd like to thank my family. One day they came home and found that their normal office working father and husband had been replaced with a stay at home writer. Worse still he was not creating something interesting like the next Harry Potter, but was instead writing ``Some boring book about money''. Despite that you have still been the most supportive and wonderful people I could ever ask for. Thank you for that, and for everything.
